---
title: "Indian Stock Market - Nifty 100"
author: "Group 1"
date: "11/16/2022"
output:
  pdf_document: default
  html_document: default
---
[Stock Market Data - Nifty 100 Stocks (1 min) data](https://www.kaggle.com/datasets/debashis74017/stock-market-data-nifty-50-stocks-1-min-data?select=1.+Data+description.txt)
```{r setup, warning=FALSE, message=FALSE, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/rachelstuder/Desktop/605Computing/Project")
```
```{r message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(stringr)
path<- getwd()
```
```{r}
myFiles <- list.files(path=path, pattern="*.csv",)
for(i in 1:length(myFiles)) {
  name<- str_split(myFiles[i], "_")[[1]][1]
  assign(name, read.csv(myFiles[i], nrows=1000))} #n=1000 for presentation purposes
```
```{r echo=FALSE}
head(ACC[,1:6], 2)
head(ADANIGREEN[,1:6], 2)
```

Our dataset contains information from **100 stock and 2 indices** (will be excluded) from the Indian Stock Market (Jan 2015 - Feb 2022). 
Each observation is a 1 minute interval. There are many other variables created that provide deeper insight to how the stocks perform, but we choose to not use these indices.

#### We focused on 6 variables of the dataset, listed below:

1) **Date** - Date of observation
2) **Open** - Open price of the index
3) **High** - High price of the index
4) **Low** - Low price of the index
5) **Close** - Close price of the index
6) **Volume** - Number of shares traded

#### Our plan for each stock file:

+ Filter only the 6 columns of interest and sort by date
+ Create day open & close prices
+ Calculate a 50 moving average
+ Find the different lengths of days when closing price is higher than the MA price
+ Calculate a mean/median duration

#### Best performing stock?
Comparing the 100 mean/median durations for **highest values**

#### Stationarity?
**Augmented Dickey-Fuller test** to evaluate for non-stationarity (evidence of trends & cycles).